### 2020-07-31 about/vita.tex
Added note to 400
Added papers to research page
Updated vita

\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmbx12  % Name

@@

\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{{#1}\hfill{#2}\par}

\leftright{\bigbold Marcel K.\ Goh}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1$\;$(438)$\;$886-2338}

@@

\leftright{\bf McGill University}{\bf September 2017 -- May 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.79/4.
\medskip
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Sorting algorithms on manifolds}{\bf May 2020 -- present}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Summer research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript.
\medskip

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of an interactive proof assistant and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medskip

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.
\medskip

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Graded MATH 235, an introductory course on the theory of groups, rings, and fields, in Fall 2019
and MATH 240, a discrete mathematics course, in Winter 2020.
\medskip

\leftright{\bf Computer Science Undergraduate Society Helpdesk}{\bf September 2018 -- present}
\leftright{\sl Tutor}{\sl Montr\'eal, QC, Canada}
\smallskip
Hold twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered include elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medskip

\filbreak % Break page here

\leftright{\bf McGill Student Emergency Response Team}{\bf October 2017 -- present}
\leftright{\sl First Responder}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date.
\medskip

\leftright{\bf Society of Undergraduate Mathematics Students}{\bf May 2019 -- January 2020}
\leftright{\sl Vice President, Academic}{\sl Montr\'eal, QC, Canada}
\smallskip
Oversaw academic affairs within SUMS council and acted as liaison between the undergraduate community and
mathematics faculty. Duties included representing the student body at department meetings and helping students with
academic concerns.
\medskip

\leftright{\bf Singapore Armed Forces}{\bf August 2015 -- August 2017}
\leftright{\sl Infantryman}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
\medskip

@@

{\bf Programming Languages}\par
OCaml, C, Haskell, Standard ML, Scheme, PostScript, Assembly, Python
\medskip

{\bf Technologies}\par
UNIX, Vim, \TeX, Git.
\medskip

{\bf Languages}\par
Fluent: English, French. Proficient: Mandarin, Italian.
\medskip

@@

Recipient of 0x\$0.40 in Knuth reward cheques.

>>>>

\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmb12  % Name
\font\tenb=cmb10
\font\mc=cmr9

\let\tenbf=\tenb

% For publication lists (adapted from Knuth's algorithms)
\newdimen\itemindent
\newif\ifitempar \itempartrue
\def\itemindentset#1{\setbox0\hbox{{\bf #1.\kern.25em}}\itemindent=\wd0\relax}
\def\pubbegin #1{\itemindentset{#11}} % when all have 1 digit
\def\ppubbegin #1{\itemindentset{#111}} % when 10 or more publications
\def\pubitem#1.{\ifitempar\smallskip\noindent\else\itempartrue
  \hskip-\parindent\fi
  \hbox to\itemindent{\bf\hfil #1.\kern.25em}%
  \hangindent=\itemindent\hangafter=1\ignorespaces}

\def\up#1{\leavevmode \raise.16ex\hbox{#1}}
\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{{#1}\hfill{#2}\par}
\def\myname{{\tensc Marcel K. Goh}}
\def\CEE{{\mc C}}
\def\UNIX{{\mc UNIX}}
\def\thing{\item{$\bullet$}}

@@

\newcount\submittedcount
\submittedcount=1
\def\subitem{\pubitem S\the\submittedcount. \global\advance\submittedcount by 1}
\newcount\reportcount
\reportcount=1
\def\repitem{\pubitem R\the\reportcount. \global\advance\reportcount by 1}

% =========== START ============ %

\leftright{\bigbold Marcel K.\ Goh}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1\thinspace\up(438\up)\thinspace 886-2338}

@@

\leftright{\bf McGill University}{\bf September 2017 -- May 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.79/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Sorting algorithms on manifolds}{\bf May 2020 -- present}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Summer research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of an interactive proof assistant and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

\sectheader{Submitted Papers}

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton-Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.

\sectheader{Reports}

\pubbegin R
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Graded MATH 235, an introductory course on the theory of groups, rings, and fields, in Fall 2019
and MATH 240, a discrete mathematics course, in Winter 2020.
\medbreak

\leftright{\bf Computer Science Undergraduate Society Helpdesk}{\bf September 2018 -- present}
\leftright{\sl Tutor}{\sl Montr\'eal, QC, Canada}
\smallskip
Hold twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered include elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medbreak

\leftright{\bf McGill Student Emergency Response Team}{\bf October 2017 -- present}
\leftright{\sl First Responder}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date.
\medbreak

\leftright{\bf Society of Undergraduate Mathematics Students}{\bf May 2019 -- January 2020}
\leftright{\sl Vice President, Academic}{\sl Montr\'eal, QC, Canada}
\smallskip
Oversaw academic affairs within SUMS council and acted as liaison between the undergraduate community and
mathematics faculty. Duties included representing the student body at department meetings,
organising midterm and final review sessions,
and helping students with
academic concerns.
\medbreak

\leftright{\bf Singapore Armed Forces}{\bf August 2015 -- August 2017}
\leftright{\sl Infantryman}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
\medbreak

@@

{\bf Programming Languages}\par
\CEE, OCaml, Haskell, Standard ML, Scheme Lisp, PostScript, {\tt CWEB}, {\tt MIXAL}, Python
\medbreak

{\bf Technologies}\par
\UNIX, Vim, \TeX, Git.
\medbreak

{\bf Languages}\par
Fluent: English, French. Proficient: Mandarin, Italian.
\medbreak

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$0.40 in Knuth reward cheques.
